\begin{acknowledgments}

    The completion of this thesis would not have been possible without the
    guidance, encouragement, and support of many people, to whom I owe a
    deep debt of gratitude.

    First and foremost, I would like to express my sincere appreciation to my
    supervisor, Professor Dr Amirhassan Monajemi, for his unwavering guidance,
    patience, and insight throughout this research. His thoughtful feedback and
    constant encouragement shaped not only this work but also the way I think
    as a researcher. I am profoundly grateful for the time and care he invested
    in mentoring me.

    I am also thankful to the members of my examination committee for their
    constructive comments and valuable suggestions, which greatly improved the
    quality of this thesis. My appreciation extends to the faculty and staff of
    the School of Computing at the National University of Singapore for fostering
    a stimulating and supportive research environment.

    I gratefully acknowledge the institutional support and resources that made
    this study possible, and I thank everyone who contributed their time and
    effort to the experiments and data that underpin this work.

    To my fellow students and labmates, thank you for the countless discussions,
    shared late nights, and good humour that made this journey both productive
    and enjoyable. I have learned a great deal from each of you.

    Finally, I dedicate my warmest thanks to my family and my partner for their endless love and
    support, from the first page to the last. This work is as much yours as it
    is mine.


\end{acknowledgments}
